---
title: "Tables and Circle Plots comparing Naive and DRTMLE group differences"
author: "MB Nebel"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup-again, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
#for tableby
library(arsenal)
library(xtable)
library(readxl)
library(circlize)
library(png)
#to remove background from .pngs
library(colordistance)
library(magick)
```

#### Define Circle plot function:
Based on [Dr. Mowinckel's](https://github.com/Athanasiamo) [tutorial](https://drmowinckels.io/blog/2018-05-25-circluar-plots-in-r-and-adding-images/) 
and adapted by [Daniel Lidstone](https://github.com/lidstone) & [Ben Risk](https://github.com/benjaminrisk) 
```{r define-circle-plot-function}
#### Function to Make Transparent Colors 
t_col <- function(color, percent = 50, name = NULL) {
  #      color = color name
  #    percent = % transparency
  #       name = an optional name for the color
  
  ## Get RGB values for named color
  rgb.val <- col2rgb(color)
  
  ## Make new color using input color as base and alpha set by transparency
  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
               max = 255,
               alpha = (100 - percent) * 255 / 100,
               names = name)
  
  ## Save the color
  invisible(t.col)
}

# varname: a variable name corresponding to a column of results.ave
# thresh: threshold to use for displaying chords

myChordDiagram = function(data,varname,alpha=0.20,alphaname,title) {
  # alpha: pvalue threshold
  # alphaname: column of data with pvalues
  
  #
  
  ## Set transparent color, used to mask unwanted chords
  trcol <- t_col("white", perc = 100, name = "white")
  
  ## Set colors for negative and positive values
  poscol <- t_col("DodgerBlue4", perc = 15, name = "lt.blue") #positive correlation color
  negcol <- t_col("red", perc = 15, name = "lt.red") #negative correlation color
  
  ## Set names for networks (netLab)
  icInfo <- read_excel("componentLabels_pca85_ica30.xlsx")
  netLab <-icInfo$cognitive.domain[icInfo$signal==1]
  
  DATA = data.frame(images = list.files("ic_pngs_noBG",full.names = T), stringsAsFactors = F) %>% 
    mutate(
      names = gsub("[a-zA-Z]|[[:punct:]]","", images),
      values = sample(0:100, size=nrow(.), replace = T)
    )
  head(DATA)
  
  # Assign group in the original data frame
  DATA$Group = netLab %>% as.factor()
  
  nGroups = length(unique(DATA$Group))
  
  #### arrange circle plot by group
  oDATA = DATA %>% arrange(Group)
  
  #### trying to avoid track text changing direction within a network
  oDATA$NewOrder = rep(NA, nrow(oDATA))
  oDATA$NewOrder[oDATA$Group=="Attn"]=7
  oDATA$NewOrder[oDATA$Group=="Control"]=1
  oDATA$NewOrder[oDATA$Group=="SalVenAtt"]=3
  oDATA$NewOrder[oDATA$Group=="CB"]=4
  oDATA$NewOrder[oDATA$Group=="Default"]=2
  oDATA$NewOrder[oDATA$Group=="SomMot"]=5
  oDATA$NewOrder[oDATA$Group=="Vis"]=6
  
  oDATA = oDATA %>% arrange(NewOrder)
  
   # Get colours, turn the vector into characters, and then use the factor numbers of DATA$NewOrder to assign colour.
  
  #cColors = wesanderson::wes_palette("FantasticFox1", nGroups, type = 'continuous')
  cColors = viridis::plasma(nGroups)
  
  oDATA$gColor = cColors[1:nGroups] %>% as.character %>% 
    .[as.numeric(oDATA$NewOrder)]
  
  #### Define small gap between ICs and big gap between networks
  # sectorGap[1] is the gap after the first sector
  # sectorGap[end] should be bigGap
  
  smallGap = 1
  bigGap = 7
  sectorGap = rep(bigGap, nrow(DATA))
  
  for (ig in 1:nrow(oDATA)-1){
    sectorGap[ig] = ifelse(oDATA$NewOrder[ig+1]==oDATA$NewOrder[ig], smallGap, bigGap)
  }
  
  ############################################
  # Create the weighted adjacency matrix:
  
  # Construct the "from" edge:
  ic.from =   substr(data$EdgeName,1,2)
  ic.from = ifelse(substr(ic.from,2,2)=='-',paste0('0',substr(ic.from,1,1)),ic.from)
  # visually check it looks good:
  cbind(data$EdgeName,ic.from)
  
  # Construct the "to" edge
  ic.to = substr(data$EdgeName,nchar(data$EdgeName)-1,nchar(data$EdgeName))
  ic.to = ifelse(substr(ic.to,1,1)=='-',paste0('0',substr(ic.to,2,2)),ic.to)
  # visually check it looks good:
  cbind(data$EdgeName,ic.to)
  
  # modify the THIRD variable to create chords for different variables:
  PAIRS = data.frame(ic.from,ic.to,data[,varname])
  
  #### Index specific pairs by a threshold
  
  neg_ix = data[,alphaname] < alpha & PAIRS[,3]<0
  pos_ix = data[,alphaname] < alpha & PAIRS[,3]>0
  
  cols = rep(trcol,nrow(PAIRS))
  cols[neg_ix]=negcol
  cols[pos_ix]=poscol
  
  ## Set plot background to white
  par(bg = 'white')
  
  ## 
  circos.par(gap.after = sectorGap)
  
  ##plot updated Chord diagram with new colors
  myPlot = chordDiagram(PAIRS, annotationTrack = c("grid"), 
                        annotationTrackHeight=c(0.05, 0.01), 
                        preAllocateTracks = list(track.height = 0.32), 
                        order=oDATA$names, grid.col = setNames(oDATA$gColor, oDATA$names), col=cols)
  title(title,col.main="black",cex.main=1.5)
  
  as_radians = function(x) x*pi/180
  
  ## Loop through images and plot brain maps
  u=0
  for(si in get.all.sector.index()){
    xplot=get.cell.meta.data("xplot",si)
    u=u+1
    
    # Small workaround because coordinate 0 should be 360
    if(xplot[1] == 0) xplot[1] = 360
    
    
    x=.86*cos(as_radians((xplot[2]+xplot[1])/2))
    y=.86*sin(as_radians((xplot[2]+xplot[1])/2))
    
    oDATA$images[grep(si, oDATA$images)] %>% 
      readPNG() %>% 
      rasterImage(x-0.09, y-0.09, x+0.09, y+0.09)
  }
  
  #### set labels to be black
  circos.track(track.index = 1, panel.fun = function(x, y) {
    xlim = get.cell.meta.data("xlim")
    xplot = get.cell.meta.data("xplot")
    ylim = get.cell.meta.data("ylim")
    sector.name = get.cell.meta.data("sector.index")
    
    circos.text(mean(xlim), ylim[1], sector.name, facing = "inside", 
                niceFacing = TRUE, adj = c(0.5, 0), col= "black")
  }, bg.border = NA)
  
  #    myPlot
}
```

#### Load results from two sets of 200 seeds
```{r load-seed-results}
results.all=NULL
for (i in 1:200) {
  load(paste0('./Results/noImputation/ic30_pc85_glm_gam_drtmle_seed',i,'.RData'))
  results.all = rbind(results.all,results.df)
}
rm(results.df)

# second set of seeds:
#Ben doesn't know why seed 365 failed
results.all2=NULL
for (i in 201:400) {
  load(paste0('./Results/noImputation/ic30_pc85_glm_gam_drtmle_seed',i,'.RData'))
  results.all2 = rbind(results.all2,results.df)
}
rm(results.df)

```

#### Compare results from two sets of 200 seeds
```{r average-two-sets}
results.ave = results.all%>%
  group_by(EdgeName)%>%
  summarize(mean.ASD.naive=mean(mean.ASD.naive), 
            mean.TD.naive=mean(mean.TD.naive),
            mean.diff.naive=mean(mean.diff.naive),
            z.stat.ASD.naive=mean(z.stat.ASD.naive),
            z.stat.TD.naive=mean(z.stat.TD.naive),
            z.stat.diff.naive=mean(z.stat.diff.naive),
            mean.ASD.SL=mean(mean.ASD.SL),
            mean.TD.SL=mean(mean.TD.SL),
            mean.diff.SL=mean(mean.diff.SL),
            z.stat.ASD.SL=mean(z.stat.ASD.SL),
            z.stat.TD.SL=mean(z.stat.TD.SL),
            z.stat.diff.SL=mean(z.stat.diff.SL),
            SL.naive.mean.diff=mean(abs(mean.diff.SL)-abs(mean.diff.naive)))

results.ave2 = results.all2%>%
  group_by(EdgeName)%>%
  summarize(mean.ASD.naive=mean(mean.ASD.naive), 
            mean.TD.naive=mean(mean.TD.naive),
            mean.diff.naive=mean(mean.diff.naive),
            z.stat.ASD.naive=mean(z.stat.ASD.naive),
            z.stat.TD.naive=mean(z.stat.TD.naive),
            z.stat.diff.naive=mean(z.stat.diff.naive),
            mean.ASD.SL=mean(mean.ASD.SL),
            mean.TD.SL=mean(mean.TD.SL),
            mean.diff.SL=mean(mean.diff.SL),
            z.stat.ASD.SL=mean(z.stat.ASD.SL),
            z.stat.TD.SL=mean(z.stat.TD.SL),
            z.stat.diff.SL=mean(z.stat.diff.SL),
            SL.naive.mean.diff=mean(abs(mean.diff.SL)-abs(mean.diff.naive)))

# compare two estimates:
plot(results.ave$z.stat.diff.SL~results.ave2$z.stat.diff.SL)
head(cbind(results.ave$z.stat.diff.SL,results.ave2$z.stat.diff.SL))

# this result appears in the manuscript:
seedCor = cor(results.ave$z.stat.diff.SL,results.ave2$z.stat.diff.SL)

```

The correlation between the average DRTMLE ASD-TD Z-statistics across the 153 edges was **`r toString(seedCor)`**. 


#### Calculate FDR adjusted p values
```{r adjust-p-values-by-set}

results.ave$p.SL = 2*(1-pnorm(abs(results.ave$z.stat.diff.SL)))
results.ave$p.SL.fdr = p.adjust(results.ave$p.SL,method='BH')

results.ave2$p.SL = 2*(1-pnorm(abs(results.ave2$z.stat.diff.SL)))
results.ave2$p.SL.fdr = p.adjust(results.ave2$p.SL,method='BH')

```

#### Compare the selected edges at FDR=0.05 in the two sets of seeds:
```{r compare-selected-edges-fdr05-across-sets}
results.ave[results.ave$p.SL.fdr<0.05,c('EdgeName')]
results.ave2[results.ave2$p.SL.fdr<0.05,c('EdgeName')]

```

`r toString(sum(results.ave$p.SL.fdr<0.05))` were selected using DRTMLE and a false discovery rate FDR=.05 in the first set of seeds and the same `r toString(sum(results.ave2$p.SL.fdr<0.05))` in the second set.


#### Compare the selected edges at FDR=0.20 in the two sets of seeds:
```{r compare-selected-edges-fdr20-across-sets}

results.ave[results.ave$p.SL.fdr<0.2,c('EdgeName')]
results.ave2[results.ave2$p.SL.fdr<0.2,c('EdgeName')]

```

`r toString(sum(results.ave$p.SL.fdr<0.2))` were selected using DRTMLE and a false discovery rate FDR=.20 in the first set of seeds and the same `r toString(sum(results.ave2$p.SL.fdr<0.2))` in the second set.

#### Average results from all seeds
```{r average-all-400-seeds}
#SL = superlearner

results.ave = rbind(results.all, results.all2) %>%
  group_by(EdgeName) %>%
  summarize(mean.ASD.naive=round(mean(mean.ASD.naive), digits = 3),
            mean.TD.naive=round(mean(mean.TD.naive), digits = 3),
            mean.diff.naive=mean(mean.diff.naive), 
            z.stat.ASD.naive=mean(z.stat.ASD.naive),
            z.stat.TD.naive=mean(z.stat.TD.naive),
            z.stat.diff.naive=round(mean(z.stat.diff.naive), digits = 3),
            mean.ASD.SL=round(mean(mean.ASD.SL), digits = 3), 
            mean.TD.SL=round(mean(mean.TD.SL), digits = 3),
            mean.diff.SL=round(mean(mean.diff.SL), digits = 3), 
            z.stat.ASD.SL=mean(z.stat.ASD.SL),
            z.stat.TD.SL=mean(z.stat.TD.SL), 
            z.stat.diff.SL=round(mean(z.stat.diff.SL), digits = 2),
            SL.naive.z.stat.diff=mean(abs(z.stat.diff.SL)-abs(z.stat.diff.naive)))

```



#### Add network names
```{r add-network-names}
icInfo <- read_excel("componentLabels_pca85_ica30.xlsx")

results.ave <- results.ave %>% 
  mutate(EdgeName = gsub("r.|ic", "", EdgeName)) %>% 
  mutate(EdgeName = gsub("[.]", "-", EdgeName)) %>% 
  mutate(ic.from = gsub("[-]", "", substr(EdgeName, 1, 2))) %>% 
  mutate(ic.to = gsub("[-]", "", substr(EdgeName, nchar(EdgeName)-1,nchar(EdgeName)))) %>% 
  mutate(net1 = icInfo$cognitive.domain[as.numeric(ic.from)]) %>% 
  mutate(net2 = icInfo$cognitive.domain[as.numeric(ic.to)])

```

#### Calculate uncorrected p values for results averaged across 400 seeds for both methods and plot histograms
```{r plot-uncorrected-p-values}
#calculate p values
results.ave$p.naive = 2*(1-pnorm(abs(results.ave$z.stat.diff.naive)))
results.ave$p.SL = 2*(1-pnorm(abs(results.ave$z.stat.diff.SL)))

pVariables = c("EdgeName", "p.naive", "p.SL")

pvalues <- reshape2::melt(results.ave[, pVariables],
                         id.vars="EdgeName",
                         variable.name = "method",
                         value.name = "p")

method.labs <- c("naive", "DRTMLE")
names(method.labs) <- c("p.naive", "p.SL")

ggplot(pvalues, aes(x=p))+
  geom_histogram(position = "identity", alpha=0.5, inherit.aes=TRUE, binwidth = .05)+
  scale_x_continuous(expand = c(0, 0))+  
  scale_y_continuous(expand = c(0, 0))+ 
  facet_grid(method~., labeller = labeller(method = method.labs))

```

#### FDR-adjusted p values
```{r adjust-p-values-reported-in-paper}
results.ave$p.naive.fdr = round(p.adjust(results.ave$p.naive,method='BH'), digits = 4)
results.ave$p.SL.fdr = round(p.adjust(results.ave$p.SL,method='BH'), digits = 4)

```

#### Determine edges showing a significant group difference FDR=.05 averaged across all 400 seeds
```{r fdr-05-edges-all-seeds}
fdr05.edges.SL = which(results.ave$p.SL.fdr<.05) 
fdr05.edges.naive = which(results.ave$p.naive.fdr<.05) 

all(fdr05.edges.naive %in% fdr05.edges.SL)

```

All edges indicated by naive approach are also indicated by DRTMLE at the FDR=0.05 level

#### Summary of network pairs showing a significant group difference using DRTMLE, FDR=.05
```{r fdr-05-table, results='asis'}
tabfdr05<- tableby(net1 ~ net2,
                 data=filter(results.ave , p.SL.fdr<.05))
summary(tabfdr05,  
        title='Network pairs showing a group difference using DRTMLE FDR=.05',digits=1, digits.p=4,digits.pct=1, numeric.simplify=TRUE, total=TRUE, test=FALSE)
```


#### Remove background from .pngs of IC maps
```{r remove-bg-from-IC-maps}
#create directory to save pngs with transparent background
dir.create("./ic_pngs_noBG")

DATA = data.frame(images = list.files("ic_pngs",full.names = T), stringsAsFactors = F) %>% 
    mutate(
      names = gsub("[a-zA-Z]|[[:punct:]]","", images),
      values = sample(0:100, size=nrow(.), replace = T)
    )
  head(DATA)

for(iimg in seq(1:nrow(DATA))) {
 img_data <- magick::image_read(DATA$images[iimg])
 new_img <- magick::image_transparent(img_data, 'black')
 fname <- sub('ic_pngs', 'ic_pngs_noBG', DATA$images[iimg])
 magick::image_write(new_img, fname)
}
  
```


#### Naive ASD-TD Z-Statistic FDR=0.05
```{r circle-naive-fdr-05, fig.width=5, fig.height=5}
png("Application_Figures/Naive_zstat_groupdifference_fdr05_noImpute.png",width=5,height=5,units="in",res=200)

myChordDiagram(data=results.ave,varname='z.stat.diff.naive',alpha=0.05,alphaname='p.naive.fdr', title='')
dev.off()

circos.clear()


```

#### DRTMLE ASD-TD Z-Statistic FDR=0.05
```{r circle-drtmle-fdr-05, fig.width=5, fig.height=5}

png("Application_Figures/DRTMLE_zstat_groupdifference_fdr05_noImpute.png",width=5,height=5,units="in",res=200)
myChordDiagram(data=results.ave,varname='z.stat.diff.SL',alpha=0.05,alphaname='p.SL.fdr',title='')
dev.off()

circos.clear()

```

#### Print a and b together for report
```{r circle-fdr-05, echo=FALSE}
myChordDiagram(data=results.ave, varname='z.stat.diff.naive', alpha=0.05, alphaname='p.naive.fdr', title='A. Naive Z-Statistic, ASD-TD, FDR=0.05')

circos.clear()

myChordDiagram(data=results.ave, varname='z.stat.diff.SL', alpha=0.05, alphaname='p.SL.fdr', title='B. DRTMLE Z-Statistic, ASD-TD, FDR=0.05')

circos.clear()

```

**Figure S3. The DRTMLE deconfounded group difference revealed more extensive differences than the naïve approach.** Z-statistics for autism spectrum disorder (ASD) versus typically developing (TD) using a) the na\"ive test and b) using DRTMLE. Connections are thresholded using a false discovery rate (FDR) of  0.05. Blue lines indicate ASD>TD (`r sum(results.ave$p.naive.fdr<.05 & results.ave$z.stat.diff.naive>0)` in naive, `r sum(results.ave$p.SL.fdr<.05 & results.ave$z.stat.diff.SL>0)` in DRTMLE). Red lines indicate ASD<TD (`r sum(results.ave$p.naive.fdr<.05 & results.ave$z.stat.diff.naive<0)` in naive,  `r sum(results.ave$p.SL.fdr<.05 & results.ave$z.stat.diff.SL<0)` in DRTMLE). Brain regions contributing to each independent component are illustrated and components are grouped by functional assignment. Navy nodes: control. Blue violet: default mode. Purple: salience/ventral attention. Magenta: pontomedullary/cerebellar. Coral: somatomotor. Orange: visual. Yellow: dorsal attention.

#### Determine edges showing a significant group difference FDR=.20
```{r fdr-20-edges}
fdr20.edges.SL = which(results.ave$p.SL.fdr<=.20) 
fdr20.edges.naive = which(results.ave$p.naive.fdr<=.20) 

all(fdr20.edges.naive %in% fdr20.edges.SL)

```
All edges indicated by naive approach are also indicated by DRTMLE at the FDR=0.2 level

#### Summary of network pairs showing a significant group difference using the naive approach, FDR=.2
```{r fdr-20-table-naive, results='asis'}
tabfdr2n<- tableby(net1 ~ net2,
                 data=filter(results.ave , p.naive.fdr<=.2))
summary(tabfdr2n,  
        title='Network pairs showing a group difference using the naive approach, FDR=.2',digits=1, digits.p=4,digits.pct=1, numeric.simplify=TRUE, total=TRUE, test=FALSE)
```

#### Summary of network pairs showing a significant group difference using DRTMLE, FDR=.2
```{r fdr-20-table-drtmle, results='asis'}
tabfdr2<- tableby(net1 ~ net2,
                 data=filter(results.ave , p.SL.fdr<=.2))
summary(tabfdr2,  
        title='Network pairs showing a group difference using DRTMLE, FDR=.2',digits=1, digits.p=4,digits.pct=1, numeric.simplify=TRUE, total=TRUE, test=FALSE)
```

#### Create table displaying group Z-statistics from DRTMLE for edges showing a group difference at FDR=.20
```{r fdr-20-table, results="asis"}
# group means for edges showing a group difference using DRTMLE:
results.ave$NetworkPair <- stringr::str_c(results.ave$net1, '-', results.ave$net2)

#results.sigEdges = results.ave[fdr20.edges.SL,c(1, 23, 2:3, 7:9,13:14, 21:22)]
results.sigEdges = results.ave[fdr20.edges.SL, c("EdgeName", "NetworkPair",
                                                 "mean.ASD.naive", "mean.TD.naive", "z.stat.diff.naive",
                                                 "mean.ASD.SL", "mean.TD.SL", "z.stat.diff.SL",
                                                 "p.naive.fdr", "p.SL.fdr")]

results.sigEdges <- results.sigEdges[order(results.sigEdges$p.naive.fdr), ]

knitr::kable(results.sigEdges, format="markdown", 
             col.names = c("Edge", "Networks", 
                           "naive ASD mean", "naive TD mean",  "naive ASD-TD Z",
                           "DRTMLE ASD mean", "DRTMLE TD mean", "DRTMLE ASD-TD Z",
                           "naive FDR-adjusted p", 
                           "DRTMLE FDR-adjusted p"))

```

DRTMLE indicates a significant deconfounded group difference for the first **`r sum(results.sigEdges$p.SL.fdr<.05)`** edges at the FDR=.05 level and an additional **`r sum(results.sigEdges$p.SL.fdr<.2 & results.sigEdges$p.SL.fdr>.05)`** edges at the FDR=.20 level.

Mean functional connectivity group estimates further from zero reflect stronger functional connectivity regardless of sign; positive scores reflect positive partial correlations, or more integrated intrinsic activity between independent components (ICs). Negative scores reflect negative partial correlations, or more segregated intrinsic activity between ICs.

#### Create version for paper
```{r fdr-20-table-paper, results='hide'}
#tab <- knitr::kable(results.sigEdges, format="latex", linesep = '')
#print(tab, type="latex")

knitr::kable(results.sigEdges, "latex", linesep = "", vline = "",
             col.names = c("Edge", "Network Pair", 
                           "naive ASD mean", "naive TD mean", "naive ASD-TD Z",
                           "DRTMLE ASD mean", "DRTMLE TD mean",  "DRTMLE ASD-TD Z",
                           "naive FDR-adjusted p", 
                           "DRTMLE FDR-adjusted p")) %>%
  #kableExtra::column_spec(9:10, width = "1 cm") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down")) %>% 
  kableExtra::as_image(width = 7, file = "Application_Figures/tableS3.pdf")

```

#### Naive ASD-TD Z-Statistic FDR=0.20
```{r circle-naive-fdr-20, fig.width=5, fig.height=5}

png("Application_Figures/Naive_zstat_groupdifference_fdr20_noImpute.png",width=5,height=5,units="in",res=200)
myChordDiagram(data=results.ave,varname='z.stat.diff.naive',alpha=0.20,alphaname='p.naive.fdr', title='')
dev.off()

circos.clear()

```

#### DRTMLE ASD-TD Z-Statistic FDR=0.20
```{r circle-drtmle-fdr-20, fig.width=5, fig.height=5}

png("Application_Figures/DRTMLE_zstat_groupdifference_fdr20_noImpute.png",width=5,height=5,units="in",res=200)
#myChordDiagram(data=results.ave,varname='z.stat.diff.SL',alpha=0.20,alphaname='p.SL.fdr',title='B. DRTMLE Z-Statistic, ASD-TD')
myChordDiagram(data=results.ave,varname='z.stat.diff.SL',alpha=0.20,alphaname='p.SL.fdr',title='')
dev.off()

circos.clear()

```

#### Print a and b together for .html
```{r circle-fdr-20, echo=FALSE}
myChordDiagram(data=results.ave,varname='z.stat.diff.naive',alpha=0.20,alphaname='p.naive.fdr',title='A. Naive Z-Statistic, ASD-TD, FDR=0.20')

circos.clear()

myChordDiagram(data=results.ave,varname='z.stat.diff.SL',alpha=0.20,alphaname='p.SL.fdr',title='B. DRTMLE Z-Statistic, ASD-TD, FDR=0.20')

circos.clear()
```


**Figure 5. The DRTMLE deconfounded group difference revealed more extensive differences than the naïve approach.** Z-statistics for autism spectrum disorder (ASD) versus typically developing (TD) using a) the na\"ive test and b) using DRTMLE. Connections are thresholded using a false discovery rate (FDR) of  0.20. Blue lines indicate ASD>TD (`r sum(results.ave$p.naive.fdr<.2 & results.ave$z.stat.diff.naive>0)` in naive, `r sum(results.ave$p.SL.fdr<.2 & results.ave$z.stat.diff.SL>0)` in DRTMLE). Red lines indicate ASD<TD (`r sum(results.ave$p.naive.fdr<.2 & results.ave$z.stat.diff.naive<0)` in naive,  `r sum(results.ave$p.SL.fdr<.2 & results.ave$z.stat.diff.SL<0)` in DRTMLE). Brain regions contributing to each independent component are illustrated and components are grouped by functional assignment. Navy nodes: control. Blue violet: default mode. Purple: salience/ventral attention. Magenta: pontomedullary/cerebellar. Coral: somatomotor. Orange: visual. Yellow: dorsal attention.


#### [Daniel Lidstone's](https://github.com/lidstone) analysis of edges indicated by DRTMLE to show a group difference at FDR=0.20

```{r lidstone-network-pairs}
SM_ix = grep('SomMot',c(icInfo$cognitive.domain))
Vis_ix = grep('Vis',c(icInfo$cognitive.domain))
CB_ix = grep('CB',c(icInfo$cognitive.domain))
Con_ix = grep('Control',c(icInfo$cognitive.domain))
Def_ix = grep('Default',c(icInfo$cognitive.domain))
Sal_ix = grep('SalVenAtt',c(icInfo$cognitive.domain))
DorAtt_ix = grep('Attn',c(icInfo$cognitive.domain))

naivefdr = results.ave[abs(results.ave$p.naive.fdr)<0.20,c('EdgeName','p.naive.fdr','z.stat.diff.naive')]
slfdr = results.ave[abs(results.ave$p.SL.fdr)<0.20,c('EdgeName','p.SL.fdr','z.stat.diff.SL')]

naivefdr_edgeNum = as.numeric(unlist((stringr::str_extract_all(naivefdr$EdgeName, "\\d+"))))
slfdr_edgeNum = as.numeric(unlist((stringr::str_extract_all(slfdr$EdgeName, "\\d+"))))

naive_SM = length((which(naivefdr_edgeNum%in%SM_ix)))
naive_Vis = length((which(naivefdr_edgeNum%in%Vis_ix)))
naive_CB = length((which(naivefdr_edgeNum%in%CB_ix)))
naive_Con = length((which(naivefdr_edgeNum%in%Con_ix)))
naive_Def = length((which(naivefdr_edgeNum%in%Def_ix)))
naive_Sal = length((which(naivefdr_edgeNum%in%Sal_ix)))
naive_DorAtt = length((which(naivefdr_edgeNum%in%DorAtt_ix)))


sl_SM = length((which(slfdr_edgeNum%in%SM_ix)))
sl_Vis = length((which(slfdr_edgeNum%in%Vis_ix)))
sl_CB = length((which(slfdr_edgeNum%in%CB_ix)))
sl_Con = length((which(slfdr_edgeNum%in%Con_ix)))
sl_Def = length((which(slfdr_edgeNum%in%Def_ix)))
sl_Sal = length((which(slfdr_edgeNum%in%Sal_ix)))
sl_DorAtt = length((which(slfdr_edgeNum%in%DorAtt_ix)))


## Bar Plot
df <- data.frame(Network = c("SMN","Visual","Subcortical","Control","Default","Ventral Attn","Dorsal Attn"), Naive = c(naive_SM,naive_Vis,naive_CB,naive_Con,naive_Def,naive_Sal,naive_DorAtt), DRTMLE = c(sl_SM,sl_Vis,sl_CB,sl_Con,sl_Def,sl_Sal,sl_DorAtt))
data.m <- reshape2::melt(df, id.vars='Network')

p <- ggplot(data=data.m, aes(x=Network, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=value), vjust=-0.1, color="black",
            position = position_dodge(0.9), size=5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()

p + labs(x="Network", y = "Number of Edges")+
  scale_fill_manual(values=c('black','lightgray'))+
  theme_classic()+theme(legend.title = element_blank(),legend.text = element_text(size=14),axis.text=element_text(size=12),
                        axis.title=element_text(size=14,face="bold"))+theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

```

